Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2020-05-29 docs/00-manuscripts/ieee/ieee-manuscript.tex
clarify scope of the study in intro

The research questions of this study are the following:

>>>>

% clarify the focus of this study
This study shows how high-dimensional datasets can be handled effectively with machine-learning methods while still being conduct inference on the fitted models.
The predictive power of non-linear methods and their ability to handle highly-correlated predictors is combined with common and new approaches for assessing feature importance and feature effects.
However, this study clearly focuses on investigating the effects of filter methods and feature set types on predictive performance rather than on interpreting feature effects.

That said, the research questions of this study are the following:
